### 2022-08-12 paper/Chapters/Chapter05.tex
update paper

\begin{figure}[th]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.32\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_error_SVD.png}
		\caption{Error}
	\end{subfigure}
	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_2_22_error.png}
		\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_32_12_error.png}
		\caption{Foreleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_42_-28_error.png}
		\caption{Hindleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}

	\decoRule
	\caption{Zoom in of some regions of Dragon object (GCNN models). (Resolution: $ 32\times32 $)}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}

	\decoRule
	\caption{Comparison of GCNN based models. (Resolution: $ 128\times 128 $)}
	\label{fig:gcnn-eval-multi-model}
\end{figure}

@@

%% CNN detail
\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-cnn.png}
		\caption{Normal Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
		\caption{Feature Map}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {1};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
	\label{fig:cnn-detail-feature-maps}
\end{figure}

%% NOC Detail
\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-noc.png}
		\caption{Normal Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
		\caption{Feature Map}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {1};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
	\label{fig:noc-detail-feature-maps}
\end{figure}

We roughly distinguish feature maps into two types. The first type of feature maps learns the details of the target object that correspond to the feature map with sparse high values. In our example, the detail areas are the tail, head, paw, etc. Using the CNN feature maps, we could see that several detail areas in a feature map have high values. For example, in Figure \ref{fig:cnn-detail-feature-maps} (b), the values in the tail, hind leg, and front leg areas of the dragon object are especially high than other areas. These high valued areas are exactly the detailed areas and the areas with higher errors in the evaluation. These feature maps show that the CNN model assigns high value to several detailed parts in a single feature map. 
In the case of the NOC model, one detailed part instead of several detailed parts is usually highly valued in a single feature map, as shown in Figure \ref{fig:noc-detail-feature-maps} (e). We can see that the hind legs are light, while other detailed areas such as the head or tail are dark. The NOC model uses one feature map to deal with only one specific detailed area. 
The GCNN model follows the patterns we found in NOC, each feature map has only one specific area that is very bright, and the rest of the areas are relatively dark. In addition, the bright area in the GCNN model is more concentrated than in the NOC model because of the skip connection, as can be seen in Figure \ref{fig:gcnn-detail-feature-maps}.

%% GCNN detail
\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-gcnn.png}
		\caption{Normal Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
		\caption{Feature Map}
	\end{subfigure}
	\begin{subfigure}[b]{0.19\linewidth}
		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
		\caption{Feature Map}
	\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {1};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
	\label{fig:gcnn-detail-feature-maps}
\end{figure}

@@

		\begin{tikzpicture}
			\node[text width=0.1\textwidth] at (11,-1) {1};
			\node[inner sep=0pt] (input) at (8,-1)
			{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
			\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
		\end{tikzpicture}
		\decoRule
		\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
		\label{fig:global-feature-maps}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_2_22_error.png}
		\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_32_12_error.png}
		\caption{Foreleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_42_-28_error.png}
		\caption{Hindleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}

	\decoRule
	\caption{Zoom in of detail regions ($ 32\times32 $) of \textit{Dragon} object (Trip-Net).}
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f3.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}

	\decoRule
	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
	\label{fig:tripnet-fusion-eval}
\end{figure}

@@

@@

\begin{figure}[th]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}
	\decoRule
	\caption{Comparison on high resolution dataset ($ 512\times 512 $).}
	\label{fig:trip-eval-compare}
\end{figure}

>>>>

\begin{figure}[th]
	\centering
	\captionsetup{width=\linewidth}
		\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_point_cloud_no_noise.png}
		\caption{Vertex}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_groundtruth.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_normal_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/svd-synthetic/no-noise/fancy_eval_22_error_SVD.png}
		\caption{Error}
	\end{subfigure}
	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_2_22_error.png}
		\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_32_12_error.png}
		\caption{Foreleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_42_-28_error.png}
		\caption{Hindleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Zoom in of some regions of Dragon object based on GCNN. (Resolution: $ 32\times32 $)}
	\label{fig:gcnn-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-GCNN.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-NOC.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_GCNN-CNN.png}
		\caption{CNN}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison of GCNN based models. (Resolution: $ 128\times 128 $)}
	\label{fig:gcnn-eval-multi-model}
\end{figure}

@@

%% global compare
\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{minipage}{0.32\linewidth}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
		\end{subfigure}

		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
			\caption{CNN}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
		\end{subfigure}
	\end{minipage}
	\begin{minipage}{0.32\linewidth}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
		\end{subfigure}

		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
			\caption{NOC}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
		\end{subfigure}

	\end{minipage}
	\begin{minipage}{0.32\linewidth}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
		\end{subfigure}

		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
			\caption{GCNN}
		\end{subfigure}
		\begin{subfigure}[t]{0.45\linewidth}
			\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
		\end{subfigure}

	\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {1};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Some of detail feature maps of CNN, NOC, GCNN models in up-sampling part on resolution $ 32\times32 $}
	\label{fig:detail-feature-maps}
\end{figure}

%% CNN detail
%\begin{figure}[H]
%	\centering
%	\captionsetup{width=\linewidth}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-cnn.png}
%		\caption{Normal Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_46.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_11.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_4.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-cnn_2.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	
%	\begin{tikzpicture}
%		\node[text width=0.1\textwidth] at (11,-1) {1};
%		\node[inner sep=0pt] (input) at (8,-1)
%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
%	\end{tikzpicture}
%	\decoRule
%	\caption{Some of feature maps of CNN model in up-sampling part on resolution $ 32\times32 $}
%	\label{fig:cnn-detail-feature-maps}
%\end{figure}

%% NOC Detail
%\begin{figure}[H]
%	\centering
%	\captionsetup{width=\linewidth}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-noc.png}
%		\caption{Normal Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_39.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_45.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_93.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-noc_104.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	
%	\begin{tikzpicture}
%		\node[text width=0.1\textwidth] at (11,-1) {1};
%		\node[inner sep=0pt] (input) at (8,-1)
%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
%	\end{tikzpicture}
%	\decoRule
%	\caption{Some of feature maps of NOC model in up-sampling part on resolution $ 32\times32 $}
%	\label{fig:noc-detail-feature-maps}
%\end{figure}
%

We roughly distinguish feature maps into two types. The first type of feature maps learns the details of the target object that correspond to the feature map with sparse high values. In our example, the detail areas are the tail, head, paw, etc. Using the CNN feature maps, we could see that several detail areas in a feature map have high values. For example, if we observe one feature map in Figure \ref{fig:detail-feature-maps} (a), the values in the tail, hind leg, and front leg areas of the dragon object are especially high than other areas. These high valued areas are exactly the detailed areas and the areas with higher errors in the evaluation. These feature maps show that the CNN model assigns high value to several detailed parts in a single feature map. 
In the case of the NOC model, one detailed part instead of several detailed parts is usually highly valued in a single feature map, as shown in Figure \ref{fig:detail-feature-maps} (b). We can see that the hind legs are light, while other detailed areas such as the head or tail are dark. The NOC model uses one feature map to deal with only one specific detailed area. 
The GCNN model follows the patterns we found in NOC, each feature map has only one specific area that is very bright, and the rest of the areas are relatively dark. In addition, the bright area in the GCNN model is more concentrated than in the NOC model because of the skip connection, as can be seen in Figure \ref{fig:detail-feature-maps} (c).

%
%%% GCNN detail
%\begin{figure}[H]
%	\centering
%	\captionsetup{width=\linewidth}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_out_gcnn-gcnn.png}
%		\caption{Normal Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_4.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_5.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_15.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	\begin{subfigure}[b]{0.19\linewidth}
%		\includegraphics[width=\linewidth]{./Figures/feature_map_gcnn/feature_map_gcnn-gcnn_127.png}
%		\caption{Feature Map}
%	\end{subfigure}
%	
%	\begin{tikzpicture}
%		\node[text width=0.1\textwidth] at (11,-1) {1};
%		\node[inner sep=0pt] (input) at (8,-1)
%		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
%		\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
%	\end{tikzpicture}
%	\decoRule
%	\caption{Some of feature maps of GCNN model in up-sampling part on resolution $ 32\times32 $}
%	\label{fig:gcnn-detail-feature-maps}
%\end{figure}
%

@@

		\begin{tikzpicture}
			\node[text width=0.1\textwidth] at (11,-1) {1};
			\node[inner sep=0pt] (input) at (8,-1)
			{\includegraphics[width=.2\textwidth]{./Figures/colorscale_deepgreen.jpg}};
			\node[text width=0.3\textwidth] at (7,-1) {Value: 0};
		\end{tikzpicture}
		\decoRule
		\caption{Some of global feature maps of CNN, NOC, GCNN models in up-sampling part on resolution $ 32\times32 $}
		\label{fig:global-feature-maps}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_22_-8_error.png}
		\caption{Scale}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_2_22_error.png}
		\caption{Head}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_32_12_error.png}
		\caption{Foreleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_42_-28_error.png}
		\caption{Hindleg}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/trip_net_zoom_in/eval_7_12_-48_error.png}
		\caption{Tail}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Zoom in of detail regions ($ 32\times32 $) of \textit{Dragon} object (Trip-Net).}
	\label{fig:tripnet-eval-synthetic-zoom-in}
\end{figure}

@@

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f1.png}
		\caption{F1}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f2.png}
		\caption{F2}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f3.png}
		\caption{F3}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/gcnn_synthetic/fancy_eval_7_error_f4.png}
		\caption{F4}
	\end{subfigure}
		\begin{tikzpicture}
		\node[text width=0.1\textwidth] at (11,-1) {90};
		\node[inner sep=0pt] (input) at (8,-1)
		{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
		\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
	\end{tikzpicture}
	\decoRule
	\caption{Comparison between different fusion times on Trip-Net Architecture ($ 128\times128 $). }
	\label{fig:tripnet-fusion-eval}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\captionsetup{width=\linewidth}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_groundtruth.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_SVD.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_NNNN-512.png}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_normal_Trip-Net-512.png}
	\end{subfigure}

	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_img.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_SVD.png}
		\caption{SVD}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_NNNN-512.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.24\linewidth}
		\includegraphics[width=\linewidth]{./Figures/comparison_512/fancy_eval_14_error_Trip-Net-512.png}
		\caption{Trip-Net}
	\end{subfigure}
	\begin{tikzpicture}
	\node[text width=0.1\textwidth] at (11,-1) {90};
	\node[inner sep=0pt] (input) at (8,-1)
	{\includegraphics[width=.2\textwidth]{./Figures/colorscale_blue.png}};
	\node[text width=0.3\textwidth] at (7,-1) {Error: 0};
\end{tikzpicture}
	\decoRule
	\caption{Comparison on high resolution dataset ($ 512\times 512 $).}
	\label{fig:trip-eval-compare}
\end{figure}

@@
